---
title: "Car Project Data Prep"
author: "Vadym Zeinalov"
format:
   html:
    toc: true
    toc-location: left
    theme: vapor
    highlight-style: breeze
    self-contained: true
---

Find what genre has the highest average positive user experiences
Find what genre has the highest average negative user experiences
Find what genre makes the most money (As revenue - budget)
Find what genre usually has the highest budgets
Find what genre has the highest average revenues 
Find movies in dataset with top 10 revenues
Find what year movies made the most money (as revenue)



## Loading Dataset

The data should be on your computer. Just locate it, using your path and everything will work


```{r}
options(scipen = 99)
```

```{r}
df <- read.delim("C:/Users/User/OneDrive - Avans Hogeschool/Desktop/Notre Dame/Grow Irish I/datawranglingpractice/movie_budget_rating.csv", fileEncoding="UTF-16LE", sep="\t", header=TRUE)
```



Find what genre has the highest average positive user experiences
```{r}

df$Metascore <- as.numeric(df$Metascore)
df <- df[!is.na(df$Metascore), ]

test_aggregate <- aggregate(Metascore ~ Genre, data = df, FUN = mean)

library(dplyr)
df %>% 
  group_by(Genre) %>% 
  summarise(avg_Metascore = mean(Metascore, na.rm = TRUE)) %>% 
  arrange(desc(avg_Metascore)) %>% 
  slice_head(n = 1)


```





Find what genre has the highest average negative user experiences
```{r}
df %>% 
  group_by(Genre) %>% 
  summarise(avg_Metascore = mean(Metascore, na.rm = TRUE)) %>% 
  arrange(avg_Metascore) %>% 
  slice_head(n = 1)
```




Find what genre makes the most money (As outcome - budget)

```{r}
df <- df %>% 
  mutate(profit = Revenue - Budget)

df %>% 
  group_by(Genre) %>% 
  summarise(profit = mean(profit, na.rm = TRUE)) %>% 
  arrange(desc(profit)) %>% 
  slice_head(n = 1)
```


Find what genre usually has the highest budgets

```{r}
df %>% 
  group_by(Genre) %>% 
  summarise(Budget = mean(Budget, na.rm = TRUE)) %>% 
  arrange(desc(Budget)) %>% 
  slice_head(n = 1)



```






Find what genre has the highest average revenues 

```{r}
df %>% 
  group_by(Genre) %>% 
  summarise(Revenue = mean(Revenue, na.rm = TRUE)) %>% 
  arrange(desc(Revenue)) %>% 
  slice_head(n = 1)
```






Find movies in dataset with top 10 revenues

```{r}
df %>% 
  arrange(desc(Revenue)) %>% 
  slice_head(n = 10)
```





Find what year movies made the most money (as revenue)
```{r}





```


